Figures to insert in text

### 2018-04-03 kanerva-answer.tex
teorema 1.2

\newtheorem{theorem}{Theorem}[section]
\usepackage{etoolbox}
\AtBeginEnvironment{theorem}{\large}

@@

So far we have looked only at a single dimension.  Let us think about how the entire bitstring is affected by this result.

@@

  \caption{The histogram was obtained through simulation. The red curve is the theoretical normal distribution found in \ref{T2}.}
  \label{fig:sdm-same-bit-histogram}
\end{figure}

>>>>

\newtheorem{theorem}{Theorem}[section]
\usepackage{etoolbox}
%\AtBeginEnvironment{theorem}{\large}

@@

So far we have looked only at a single pair of bitstrings, the probability of a single bitmatch between bitstrings within the access radius distance.  Now let us consider the number of activated hard locations exhibiting this bitmatch.

@@

  \caption{Given an address $x$ and a dimension $i$, how many hard locations with bitmatches in $i$ are activated by reading at $x$?  The histogram was obtained through numerical simulation. The red curve is the theoretical normal distribution found in Theorem \ref{T2}.}
  \label{fig:sdm-same-bit-histogram}
\end{figure}
